---
title: "pall_modulescore"
output: html_document
date: "2023-10-23"
---

```{r}
library(Seurat)
library(qs)
library(dplyr)
library(tidyverse)
library(BiocParallel)
library(ggplot2)
library(viridis)
library(viridisLite)
```
```{r}
#load HCA gene list as mentioned in the paper
HCA_genes <- read.xlsx("/HCA_celltypes.xlsx")
```

```{r}
#extract gene signatures from HCA


HSC_genes_list <- list(HSC_genes)

MPP_genes_list <- list(MPP_genes)

GMP_genes_list <- list(GMP_genes)

Mono_CD14_genes_list <- list(Mono_CD14_genes)

Mono_CD16_genes_list <- list(Mono_CD16_genes)

pre_DC_genes_list <- list(pre_DC_genes)

cDC1_genes_list <- list(cDC1_genes)

cDC2_genes_list <- list(cDC2_genes)

prMA_genes_list <- list(prMA_genes)

eo_genes_list <- list(eo_genes)
```

```{r}
```{r}
p4760_ms_I <- subset(pall, idents ="Tumor_P4760_clusterI")

p4760_ms_II <- subset(pall, idents="Tumor_P4760_clusterII")
modulescorelist <- list(HSC_genes_list,MPP_genes_list,GMP_genes_list,Mono_CD14_genes_list,Mono_CD16_genes_list,pre_DC_genes_list,cDC1_genes_list,cDC2_genes_list,prMA_genes_list,eo_genes_list)
for(modulescore_name in names(modulescorelist)){
   p4760_ms_I <- AddModuleScore(p4760_ms_I,
                                 features = modulescorelist[[modulescore_name]],
                                 nbin=16,
                                 name=modulescore_name)
}


for(modulescore_name in names(modulescorelist)){
   p4760_ms_II <- AddModuleScore(p4760_ms_II,
                                 features = modulescorelist[[modulescore_name]],
                                 nbin=16,
                                 name=modulescore_name)
}

pall_modulescores<- #repeat for all tumor clusters
```

```{r}
plot_HCA<- VlnPlot(pall_modulescores, features = c( "HSC_genes1","GMP_genes1", "MPP_genes1","Mono_CD14_genes1","pre_DC_genes1","cDC1_genes1","cDC2_genes1", "prMA_genes1", "eo_genes1"), ncol = 3, pt.size = 0)
```
