---
title: "pall_DEG_05"
output: html_document
date: "2023-10-23"
---
```{r}
library(dplyr)
library(Seurat)
library(ggplot2)
library(sctransform)
library(qs)
library(patchwork)
library(openxlsx)
library(tidyverse)
library(BiocParallel)
library(pheatmap)
library(viridis)
library(viridisLite)
```

```{r}
#load seurat object with cells from all the clusters
pall <- subset(pall, idents = c("p1000_tumor","p1001_tumor", "p1002_tumor_clusterI", "p1002_tumor_clusterII","p1072_tumor_clusterI","p1072_tumor_clusterII"))
```


```{r}
```{r}
pall.markers<-FindAllMarkers(pall, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
pall.markers %>% group_by(cluster) %>% top_n(n = 150, wt = avg_log2FC)
```

```{r}
top50 <- pall.markers %>% group_by(cluster) %>% top_n(n = 50, wt = avg_log2FC)
top150 <- pall.markers %>% group_by(cluster) %>% top_n(n = 150, wt = avg_log2FC)
```


```{r}
heatmap_top50 <-DoHeatmap(plinda_4760, features = top50$gene) + NoLegend() + scale_fill_gradient2(low="blue", high="red", mid = "white")
heatmap_top150 <-DoHeatmap(plinda_4760, features = top150$gene) + NoLegend() + scale_fill_gradient2(low="blue", high="red", mid = "white")
```

```{r fig.width=35, fig.height=35}
heatmap_top50
```

```
