---
title: "pall_singleR_02"
output: html_document
date: "2023-10-23"
---

```{r}
library(Seurat)
library(qs)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(sctransform)
library(patchwork)
library(SingleR)
library(openxlsx)
library(tidyverse)
library(BiocParallel)
library(pheatmap)
library(viridis)
library(viridisLite)
```

```{r}


#pall<-load seurat objects with cell type annotations


pall <- subset(pall, idents=c("Tumor_P1000","Tumor_P1001","Tumor_P1002_clusterI","Tumor_P1002_clusterII","Tumor_P1072_clusterI","Tumor_P1072_clusterII","Tumor_P4760_clusterI","Tumor_P4760_clusterII"))


```

```{r}
#load HCA reference
hca_small <- qread("/HCA_integrated_5_subsample.qs")
hca_counts <- hca_small@assays[["SCT"]]@data

```

```{r}
#Run singleR for all tumor cells 

#load the counts
pall_counts <- pall@assays[["SCT"]]@data

#Run SingleR with following parameters
all_2_pred <- SingleR(  test = pall_counts,
                        ref = hca_counts,
                        labels = hca_small[["celltype_1"]][[1]],
                        de.method="wilcox",
                        BPPARAM=MulticoreParam(10))

pall_tumors <- AddMetaData(pall_tumors, metadata = all_2_pred_SCT[["pruned.labels"]], col.name = "celltype_1_predicted")
scores <- data.frame(all_2_pred_SCT[["scores"]])
colnames(scores) <- paste0(colnames(scores),"_pred_score")
rownames(scores) <- colnames(pall_tumors)
pall_tumors <- AddMetaData(pall_tumors, scores)
#save the dataobject
qsave(pall_tumors, /pall_singleRpred.qs"))
```

```{r}
DimPlot(pall_tumors, group.by = "celltype_1_predicted", label = T) + 
        NoLegend() + 
        ggtitle(paste0(pall_tumors[["orig.ident"]][[1]], " Assigned celltypes"))



umap_celltype_prediction <- DimPlot(pall, reduction = "umap", group.by="celltype_1_predicted",cols=palette,order=my_order,label = T,pt.size=0.5)+ggtitle("Predicted celltypes")


qsave(pall, "/pall_singleR_2.qs")

```

```{r}

```{r}
#For pie charts
pall<- qread("/pall_singleR_2.qs")
#subset tumor clusters
p4760_cI<- subset(pall, idents = "Tumor_P4760_clusterI")
p4760_cII<- subset(pall, idents = "Tumor_P4760_clusterII")
# subset tumor cluster from all the samples

```

```{r}
#for p4760

sort(table(p4760_cI$celltype_1_predicted))
cellnumber_p4760_cI <- c(25,64,129,506)
celltype_p4760_cI <- c("prMono","cDC2","Mono/Macro_CD16","Mono/Macro_CD14")
pie_4760_df_cI <- data.frame(cellnumber_p4760_cI, celltype_p4760_cI)


sort(table(p4760_cII$celltype_1_predicted))
cellnumber_p4760_cII <- c(68,74,92,116, 180)
celltype_p4760_cII <- c("prMA","HSC","ERP","MPP","Other")
pie_4760_df_cII <- data.frame(cellnumber_p4760_cII, celltype_p4760_cII)
```

```{r}
# Create a basic bar
pie_4760_cI<-  ggplot(pie_4760_df_cI, aes(x="", y=cellnumber_p4760_cI, fill=celltype_p4760_cI)) + geom_bar(stat="identity", width=1)

# Convert to pie (polar coordinates) 
pie_4760_cI <- pie_4760_cI + coord_polar("y", start=0) + geom_text(aes(label = paste0(cellnumber_p4760_cI,
                               "(",
                               scales::percent(round(cellnumber_p4760_cI / sum(cellnumber_p4760_cI),digits=1)),
                               ")")), color="black", position = position_stack(vjust = 0.5))

#same for all other tumor clusters
```

